Fast solvers for the high-order FEM simplicial de Rham complex \thanks{Submitted to the editors July XX, 2024. \funding{ PDB and PEF were supported by EPSRC grant EP/W026260/1. } }

### 2024-06-27 paper/paper.tex
Sketch section 3

\section{Design of preconditioners}

We follow 
the low-order space decompositions studied in \cite{arnold00}
and extend them to high-order with static-condensation.

@@

\begin{figure}
\footnotesize
\centering
\begin{tikzpicture}[%
 every node/.style={draw=black, thick, anchor=west},
grow via three points={one child at (-0.0,-0.7) and
	two children at (0.0,-0.7) and (0.0,-1.4)},
edge from parent path={(\tikzparentnode.210) |- (\tikzchildnode.west)}]
\node {KSP: Conjugate Gradients}
   child {node {PC: Two-level vertex-star additive Schwarz}
   child {node {$p$-fine: Interior-facet additive decomposition}
      child {node {Interior: point-Jacobi}}
      child {node {Facet: vertex-star patches}}
   }
   child[missing]{}
   child[missing]{}
   child {node {$p$-coarse ($p=1$): Cholesky}
      %child {node {Relaxation: Hiptmair--Jacobi}}
      %child {node {$h$-coarse: Cholesky}}
   }
};
\end{tikzpicture}
\caption{Solver diagram for $\Hgrad$ using the interior-facet decomposition.}
\end{figure}

>>>>

\section{Design of preconditioners}
In this section we desribe the solver components and their computational complexities.

\begin{itemize}
\item The bases described above present weak coupling between the interior and facet degrees of freedom.
\item We propose a block diagonal preconditioner that only assembles the facet block, and only requires the diagonal entries of the interior block.
\item The Krylov solver only requires matrix-free operation evaluation and preconditioner application. It is not evident that these bases expose structure for sum-factorization as the Bernstein--Bezier bases, hence operator application requires $\bigo{p^{2d}}$ flops and $\bigo{p^{2d}}$ storage. The storage cost here comes from tabulating the basis and its derivatives onto the quadrature points on the reference cell and does not scale with the number of cells.
\item The facet cell submatrices have $\bigo{p^{2(d-1)}}$ entries, and cost $\bigo{p^{3(d-1)}}$ flops to assemble. 
The solution of a patch problem on the facets involves the factorization of the patch matrix, which requires $\bigo{p^{2(d-1)}}$ storage and $\bigo{p^{3(d-1)}}$ flops top compute, solving the patch subproblems at each Krylov iteration incurs $\bigo{p^{2(d-1)}}$ flops per patch. 
\item In three dimensions the costs of operator application and preconditioner setup and application balance to $\bigo{p^6}$ flops and $\bigo{p^4}$ storage.
\end{itemize}

\subsection{Choice of space decompositions}
We follow 
the low-order space decompositions studied in \cite{arnold00}
and extend them to high-order with static-condensation.

@@

\begin{figure}[htbp]
\footnotesize
\centering
\begin{tikzpicture}[%
 every node/.style={draw=black, thick, anchor=west},
grow via three points={one child at (-0.0,-0.7) and
	two children at (0.0,-0.7) and (0.0,-1.4)},
edge from parent path={(\tikzparentnode.210) |- (\tikzchildnode.west)}]
\node {KSP: Conjugate Gradients}
   child {node {PC: Two-level vertex-star additive Schwarz}
   child {node {$p$-fine: Interior-facet additive decomposition}
      child {node {Interior: point-Jacobi}}
      child {node {Facet: vertex-star patches}}
   }
   child[missing]{}
   child[missing]{}
   child {node {$p$-coarse ($p=1$): Cholesky}
      %child {node {Relaxation: Hiptmair--Jacobi}}
      %child {node {$h$-coarse: Cholesky}}
   }
};
\end{tikzpicture}
\caption{Solver diagram for $\Hgrad$ using the interior-facet decomposition.}
\end{figure}
